Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-16 nlp.tex
More typo fixes

While there are several functionally equivalent notations for representing CFG, we use the \textit{Backus-Naur Form} (BNF) for defining the grammar rules for \dateparse formats. In particular, we use the \textit{Extended Backus-Naur Form} (EBNF) as the notation is more compact and readable for frequently used constructions~\cite{Grune:1990}. We use a Cocke-Younger-Kasami (CYK) parser for syntactically parsing a column of date-time strings based on the grammar~\cite{Cocke:1969,Younger67,Kasami:1965}. The parser is a dynamic programming algorithm that identifies the highest probable syntactic parse trees, given the grammar and an input date-time string.

@@

In the context of CFGs, probabilities have been used to define a probability distribution over a set of parse trees defined by the CFG, and are a useful method for modeling such ambiguity~\cite{Collins:2003,Manning:1999}. The resulting formalism called Probabilistic Context-Free Grammar (PCFG), extends the CFG by assigning probabilities to the production rules of the grammar. During the process of parsing the date-time pattern, the probabilities are used as a filtering mechanism to rank the pattern(s) that a given string resolves to in the grammar.

@@

Having defined initial probabilistic weights to the \texttt{PCFG}, we employ supervised learning with a known training set of date time formats to estimate the rule probabilities.  The training corpus is a set of files obtained from an online data analysis corpus, described in Section 5.

>>>>

While there are several functionally equivalent notations for representing CFG, we adopt the \textit{Backus-Naur Form} (BNF) for defining the grammar rules for \texttt{DATEPARSE} formats. In particular, we use the \textit{Extended Backus-Naur Form} (EBNF) as the notation is more compact and readable for frequently used constructions~\cite{Grune:1990}. We employ a Cocke-Younger-Kasami (CYK) parser for syntactically parsing a column of date-time strings based on the grammar~\cite{Cocke:1969,Younger67,Kasami:1965}. The parser is a dynamic programming algorithm that identifies the highest probable syntactic parse trees, given the grammar and an input date-time string.

@@

In the context of CFGs, probabilities have been used to define a probability distribution over a set of parse trees defined by the CFG, and are a useful method for modeling such ambiguity~\cite{Collins:2003,Manning:1999}. The resulting formalism called \textit{Probabilistic Context-Free Grammar} (PCFG), extends the CFG by assigning probabilities to the production rules of the grammar. During the process of parsing the date-time pattern, the probabilities are used as a filtering mechanism to rank the pattern(s) that a given string resolves to in the grammar.

@@

Having defined initial probabilistic weights to the \texttt{PCFG}, we employ supervised learning with a known training set of date time formats to estimate the rule probabilities.  The training corpus is a set of files obtained from an online data analysis corpus, described in Section 6.

### 2015-07-16 testing.tex
More typo fixes

Further manual tagging focused on the files most likely to represent dates. Many of the files in the collection are not actually dates, such as fields named ``updated by'' (which contain ``date''). A random sample of 850 columns named exactly ``date'', ``time'' or ``month'' (case-insensitive) were manually judged.

@@

Some of the dates are clearly just numbers, but our approach is to assume that when the user tells us that the column contains dates we should find the best fit. The samples include dates from a wide range of historical sources (\eg Roman pottery dates) so we have elected to defer the date identification task to the user.

>>>>

Further manual tagging focused on the files most likely to represent dates. Many of the files in the collection are not actually dates, such as fields named ``updated by'' (which contain ``date''). A random sample of 850 columns named exactly ``date'', ``time'' or ``month'' (case-insensitive) were manually judged.\\

@@

Some of the dates are clearly just numbers, but our approach is to assume that when the user tells us that the column contains dates we should find the best fit. The samples include dates from a wide range of historical sources (\eg Roman pottery dates) so we have elected to defer the date identification task to the user.\\\\s
